Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-09 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Fix typo
Reviewer 2; comment D2: clarify novel aspects of the calculus in the introduction

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The higher-order modal natural deduction calculus proposed here has special introduction and elimination rules for modalities, as defined in Section \ref{sec:calculus}, and is sound and complete relative to an axiomatic modal calculus, as proven in Section \ref{sec:compl-sound}.

The natural deduction style was chosen for three reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiar with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this \citep{CSRModalLogicCoq}.

>>>>

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The natural deduction calculus proposed and used in this paper is an extension of a standard natural deduction calculus for (non-modal) higher-order logic \citep{BezmuellerBrownKohlhase} with new introduction and elimination rules for modal operators (as presented in Section \ref{sec:calculus}). This calculus is sound and complete relative to the non-modal calculus extended with Axiom K and the Necessitation rule (as demonstrated in Subsection \ref{sec:compl-sound}).

The higher-order modal natural deduction calculus proposed here has special introduction and elimination rules for modalities, as defined in Section \ref{sec:calculus}, and is sound and complete relative to an axiomatic modal calculus, as proven in Section \ref{sec:compl-sound}.

The natural deduction style was chosen for three reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiarized with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this \citep{CSRModalLogicCoq}.
